LANGuage IDentification

### 2024-12-18 paper/paper.tex
paper reviewed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{bm}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{blindtext}
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{colorlinks,
           %citecolor=black,
           %filecolor=black,
           %linkcolor=black,
           %urlcolor=black,
           bookmarksopen=true}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt,
defernumbers=true
]{biblatex}
\DeclareBibliographyCategory{cited}
\AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}
\addbibresource{references.bib}
\usepackage{bookmark}
\usepackage{enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\copyrightnotice}
\setlength{\headheight}{14.5pt}
%\addtolength{\topmargin}{-2.5pt}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\usepackage{float}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

        The project repository is available at: \\
        \url{https://github.com/Marado-Programmer/langid}
    \end{abstract}

@@

    The way I implemented the BoW was by reading a file and collect every
    single word from it separated by white spaces, dashes, punctuation,
    parenthesis or quotation marks and then spit to \texttt{stdout} a formatted
    vocabulary, so you can pipe it later or write it to a file. Words are
    case-sensitive, and it's possible to create the vocabulary in alphabetic
    order.

@@

    Because I couldn't find a simple way of doing anonymous functions in my
    language of choice, \href{run:../src/utils/neural.zig}{my implementation}
    does not allow specifying basis functions nor activation functions so every
    basis function can be thought as being the identify function $
    \mathbf{\phi}(x) = x $ and the activation function can be toggled between
    the identify and sigmoid \eqref{eq:sigmoid}.

@@

    Because a neuron is really just a function, a neuron can be a basis
    function of another neuron, starting a network.

    %%% create visual representation of the above

    A network is composed of layers, each with its own number of neurons.

    %%% visual representation of a layer

    Each of neuron will create a value called \textbf{activation} represented
    by $ a_{j} $ \eqref{eq:activation} where $ j $ is the neuron number (we can
    think of a layer as a column matrix of neurons), $ \mathbf{X} $ is the
    function input or the activations from the layer before after they passed
    through an activation function and $ D $ is the amount of row in $
    \mathbf{x} $ $ - 1 $.

@@

    \begin{equation}
        Y_{0} = \textbf{x}
    \end{equation}
    \begin{equation}
        Y_{n} = f_{n} \left( Y_{n - 1}^{T} \cdot w^{(n)} \right), n > 0
    \end{equation}

@@

    %%% visual representation of a neural network

    Layers and neural network representation can be found
    \href{run:../src/utils/neural.zig}{\texttt{/src/utils/neural.zig}}.

    %%% create x^2 sin(x) |x|

@@

    \begin{equation}
        \begin{split}
            \mathbf{w}^{\left( \tau + 1 \right)} & = \mathbf{w}^{\left( \tau \right)} + \Delta \mathbf{w}^{\left( \tau \right)} = \\
            & = \mathbf{w}^{\left( \tau \right)} + \left( \left( \mathbf{w}^{\left( \tau \right)} + \eta \nabla E \left( \mathbf{w}^{\left( \tau \right)} \right) \right) - \mathbf{w}^{\left( \tau \right)} \right) = \\
            & = \mathbf{w}^{\left( \tau \right)} + \eta \nabla E \left( \mathbf{w}^{\left( \tau \right)} \right)
        \end{split}
        \label{eq:gradient_descent_optimization}
    \end{equation}

@@

    We have a general error function which is the sum of the errors of each
    input data.

    \begin{equation}
        E \left( \mathbf{w} \right) = \displaystyle\sum_{n=1}^{N} E_{n}(\mathbf{w})
    \end{equation}

@@

    So we start by feeding forward where we calculate all the activations for
    every input $ \mathbf{x}_{i} $. In all the equations forward $ \left( \tau
    \right) $ represents the layer.

    Remember from the equation \eqref{eq:linear_model}. Here we have

@@

    \newcommand{\pd}[2]{\frac{\partial {#1}}{\partial {#2}}}
    \newcommand{\ajl}{a_{j^{\nlayer}}^{\nlayer}}
    \newcommand{\ajpl}[1]{a_{j^{\npblayer{#1}}}^{\npblayer{#1}}}
    Now as we did before, we want to calculate the gradient, so we need to
    calculate the partial derivative $ \pd{E_{n}}{w_{ji}^{\nlayer}} $ for every
    weight.

@@

    \begin{equation}
        \pd{E_{n}}{w_{ji}^{\nlayer}} = \pd{E_{n}}{a_{j}^{\nlayer}} \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}}
    \end{equation}

@@

    \begin{equation}
        \begin{split}
            \pd{E_{n}}{a_{j}^{\nlayer}} & = \pd{}{a_{j}^{\nlayer}} \left( a_{j}^{\left( \tau \right)} - t_{j} \right)^{2} = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) \pd{}{a_{j}^{\nlayer}} \left( a_{j}^{\left( \tau \right)} - t_{j} \right) = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) \left( 1 \right) = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) = \\
            & = \delta_{j}
        \end{split}
    \end{equation}
    \begin{equation}
        \begin{split}
            \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}} & = \pd{}{w_{ji}^{\nlayer}} \displaystyle\sum_{i} \left( w_{ji}^{\nlayer} z_{i}^{\nplayer{1}} \right) = \\
            & = \pd{}{w_{ji}^{\nlayer}} \left( w_{ji}^{\nlayer} z_{i}^{\nplayer{1}} + \displaystyle\sum_{k \neq i} \left( w_{jk}^{\nlayer} z_{k}^{\nplayer{1}} \right) \right) = \\
            & = \left( 1 \right) z_{i}^{\nplayer{1}} + \displaystyle\sum_{k \neq i} 0 = \\
            & = z_{i}^{\nplayer{1}}
        \end{split}
    \end{equation}

    \begin{equation}
        \pd{E_{n}}{w_{ji}} = \delta_{j}^{\nlayer} z_{i}^{\nplayer{1}}
    \end{equation}

    We call $ \delta_{j}^{\nlayer} $ the errors. Because we already calculated
    every $ z_{i}^{\nplayer{1}} $ while forward propagating, we really just
    need to calculate the errors.

    The $ \delta_{j}^{\nlayer} $ we calculated is for the output layer. For the
    layer before that, we can also use the chain rule.

    \begin{equation}
        \begin{split}
            \delta_{j}^{\nplayer{1}} & = \pd{E_{n}}{a_{j}^{\nplayer{1}}} \\
            & = \displaystyle\sum_{k} \left( \pd{E_{n}}{a_{k}^{\nlayer}} \pd{a_{k}^{\nlayer}}{a_{j}^{\nplayer{1}}} \right) = \\
            & = \displaystyle\sum_{k} \left( \delta_{k}^{\nlayer} \pd{}{a_{j}^{\nplayer{1}}} \left( w_{kj}^{\nlayer} f^{\nplayer{1}} \left( a_{j}^{\nplayer{1}} \right) + \displaystyle\sum_{i \neq j} \left( w_{ki}^{\nlayer} z_{ki}^{\nplayer{1}} \right) \right) \right) = \\
            & = \displaystyle\sum_{k} \left( \delta_{k}^{\nlayer} w_{ki}^{\nlayer} f^{\prime \nplayer{1}} \left( a_{i}^{\nplayer{1}} \right)  \right) = \\
            & = f^{\prime \nplayer{1}} \left( a_{j}^{\nplayer{1}} \right) \displaystyle\sum_{k} \left( w_{kj}^{\nlayer} \delta_{k}^{\nlayer} \right)
        \end{split}
    \end{equation}

@@

    We may also accumulate gradients to apply it to the weights all at once.

    \begin{equation}
        \pd{E}{w_{ji}^{\nlayer}} = \displaystyle\sum_{n} \pd{E_{n}}{w_{ji}^{\nlayer}}
    \end{equation}

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{bm}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{blindtext}
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{colorlinks,
           %citecolor=black,
           %filecolor=black,
           %linkcolor=black,
           %urlcolor=black,
           bookmarksopen=true}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt,
defernumbers=true
]{biblatex}
\DeclareBibliographyCategory{cited}
\AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}
\addbibresource{references.bib}
\usepackage{bookmark}
\usepackage{enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\copyrightnotice}
\setlength{\headheight}{14.5pt}
%\addtolength{\topmargin}{-2.5pt}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{gnuplot-lua-tikz}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

        The project repository is available at: \\
        \url{https://github.com/Marado-Programmer/langid} \cite{repo}
    \end{abstract}

@@

    The way I implemented the Bag of Words was by reading a file and collect
    every single word from it separated by white spaces, dashes, punctuation,
    parenthesis or quotation marks and then spit to \texttt{stdout} a formatted
    vocabulary, so you can pipe it later or write it to a file. Words are
    case-sensitive, and it's possible to create the vocabulary in alphabetic
    order.

@@

    Because I couldn't find a simple way of doing anonymous functions in my
    language of choice, \href{run:../src/utils/neural.zig}{my implementation}
    does not allow specifying basis functions so every
    basis function can be thought as being the identify function $
    \mathbf{\phi}(x) = x $, but the activation functions can be specified via
    an enumeration value which gives a set of options like \eqref{eq:sigmoid}
    for example.

@@

    Because a neuron is really just a function, a neuron can be a basis
    function of another neuron, starting a network~\ref{fig:neurons_connecting}.

    \begin{figure}
        \begin{center}
            \begin{tikzpicture}[
                    neuron/.style={circle, draw=black!90, very thick},
                    var/.style={}, io/.style={circle, draw=black!90,
                    fill=black!10, very thick, minimum size=7mm},
                ]
                \node[neuron] (neuron_1) {1};
                \node[neuron] (neuron_2) [right=of neuron_1] {2};
                \node[var] (input) [left=of neuron_1] {$ \mathbf{x} $};
                \node[var] (output) [right=of neuron_2] {$ y $};

                \draw[->] (input.east) -- (neuron_1.west);
                \draw[->] (neuron_1.east) -- (neuron_2.west);
                \draw[->] (neuron_2.east) -- (output.west);
            \end{tikzpicture}
        \end{center}
        \caption{Neuron 1 working as a basis function for neuron 2.}\label{fig:neurons_connecting}
    \end{figure}

    A network~\ref{fig:network} is composed of layers, each with its own number of neurons.

    Each one of the neurons will create a value called \textbf{activation}
    represented by $ a_{j} $ \eqref{eq:activation} where $ j $ is the neuron
    number (we can think of a layer as a column matrix of neurons), $
    \mathbf{X} $ is the function input or the activations from the layer before
    after they passed through an activation function and $ D $ is the amount of
    row in $ \mathbf{x} $ $ - 1 $.

@@

    \begin{equation}
        Y_{0} = \mathbf{x}
    \end{equation}
    \begin{equation}
        Y_{n} = f_{n} \left( Y_{n - 1}^{T} \cdot w^{(n)} \right), n > 0
    \end{equation}

@@

    \begin{figure}
        \begin{center}
            \begin{tikzpicture}[
                    neuron/.style={circle, draw=black!90, very thick},
                    var/.style={}, io/.style={circle, draw=black!90,
                    fill=black!10, very thick, minimum size=7mm},
                ]
                \node[neuron] (neuron_1_1) {};
                \node[neuron] (neuron_1_2) [below=of neuron_1_1] {};
                \node[neuron] (neuron_1_3) [below=of neuron_1_2] {};
                \node[neuron] (neuron_1_4) [below=of neuron_1_3] {};
                \node[neuron] (neuron_1_5) [below=of neuron_1_4] {};
                \node[neuron] (neuron_2_1) [right=2cm of neuron_1_2] {};
                \node[neuron] (neuron_2_2) [right=2cm of neuron_1_4] {};
                \node[var] (input_m) [left=2cm of neuron_1_3] {$ \vdots $};
                \node[var] (input_i) [above=of input_m] {$ \mathbf{x}_{1} $};
                \node[var] (input_f) [below=of input_m] {$ \mathbf{x}_{D} $};
                \node[var] (output) [below right=of neuron_2_1] {$ y $};
                \node[var] (layer1) [above=of neuron_1_1] {1\textsuperscript{st} layer};
                \node[var] (layer2) [above=of neuron_2_1] {2\textsuperscript{nd} layer};

                \draw[->] (input_i.east) -- (neuron_1_1.west);
                \draw[->] (input_i.east) -- (neuron_1_2.west);
                \draw[->] (input_i.east) -- (neuron_1_3.west);
                \draw[->] (input_i.east) -- (neuron_1_4.west);
                \draw[->] (input_i.east) -- (neuron_1_5.west);
                \draw[->] (input_f.east) -- (neuron_1_1.west);
                \draw[->] (input_f.east) -- (neuron_1_2.west);
                \draw[->] (input_f.east) -- (neuron_1_3.west);
                \draw[->] (input_f.east) -- (neuron_1_4.west);
                \draw[->] (input_f.east) -- (neuron_1_5.west);
                \draw[->] (neuron_1_1.east) -- (neuron_2_1.west);
                \draw[->] (neuron_1_1.east) -- (neuron_2_2.west);
                \draw[->] (neuron_1_2.east) -- (neuron_2_1.west);
                \draw[->] (neuron_1_2.east) -- (neuron_2_2.west);
                \draw[->] (neuron_1_3.east) -- (neuron_2_1.west);
                \draw[->] (neuron_1_3.east) -- (neuron_2_2.west);
                \draw[->] (neuron_1_4.east) -- (neuron_2_1.west);
                \draw[->] (neuron_1_4.east) -- (neuron_2_2.west);
                \draw[->] (neuron_1_5.east) -- (neuron_2_1.west);
                \draw[->] (neuron_1_5.east) -- (neuron_2_2.west);
                \draw[->] (neuron_2_1.east) -- (output.west);
                \draw[->] (neuron_2_2.east) -- (output.west);
            \end{tikzpicture}
        \end{center}
        \caption{Two layer neural network, first layer has 5 neurons and the
        second one 2.}\label{fig:network}
    \end{figure}

    Layers and neural network representation can be found \\
    \href{run:../src/utils/neural.zig}{\texttt{/src/utils/neural.zig}}.

@@

    \begin{equation}
        \begin{split}
            \mathbf{w}^{\left( \tau + 1 \right)} & = \mathbf{w}^{\left( \tau \right)} + \Delta \mathbf{w}^{\left( \tau \right)} = \\
            & = \mathbf{w}^{\left( \tau \right)} + \left( \left( \mathbf{w}^{\left( \tau \right)} - \eta \nabla E \left( \mathbf{w}^{\left( \tau \right)} \right) \right) - \mathbf{w}^{\left( \tau \right)} \right) = \\
            & = \mathbf{w}^{\left( \tau \right)} - \eta \nabla E \left( \mathbf{w}^{\left( \tau \right)} \right)
        \end{split}
        \label{eq:gradient_descent_optimization}
    \end{equation}

@@

    We have a general error function which is the sum of the errors of each
    input data \eqref{eq:general_error_function}.

    \begin{equation}
        E \left( \mathbf{w} \right) = \displaystyle\sum_{n=1}^{N} E_{n}(\mathbf{w})
        \label{eq:general_error_function}
    \end{equation}

@@

    So we start by feeding forward where we calculate all the activations for
    every input $ \mathbf{x}_{i} $. In all the equations forward $ \left( \tau
    \right) $ represents the layer $ \tau $ being the last layer.

    Remember from the equation \eqref{eq:neuron}. Here we have

@@

    \newcommand{\pd}[2]{\frac{\partial {#1}}{\partial {#2}}}
    \newcommand{\ajl}{a_{j^{\nlayer}}^{\nlayer}}
    \newcommand{\ajpl}[1]{a_{j^{\npblayer{#1}}}^{\npblayer{#1}}}
    Now as we did before, we want to calculate the gradient, so we need to
    calculate the partial derivative $ \pd{E_{n}}{w_{ji}^{\nlayer}} $
    \eqref{eq:weight_partial_derivative} for every weight.

@@

    \begin{equation}
        \pd{E_{n}}{w_{ji}^{\nlayer}} = \pd{E_{n}}{a_{j}^{\nlayer}} \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}}
        \label{eq:weight_partial_derivative}
    \end{equation}

@@

    \begin{equation}
        \begin{split}
            \pd{E_{n}}{a_{j}^{\nlayer}} & = \pd{}{a_{j}^{\nlayer}} \left( a_{j}^{\left( \tau \right)} - t_{j} \right)^{2} = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) \pd{}{a_{j}^{\nlayer}} \left( a_{j}^{\left( \tau \right)} - t_{j} \right) = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) \left( 1 \right) = \\
            & = 2 \left( a_{j}^{\left( \tau \right)} - t_{j} \right) = \\
            & = \delta_{j}
        \end{split}
        \label{eq:errors}
    \end{equation}
    \begin{equation}
        \begin{split}
            \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}} & = \pd{}{w_{ji}^{\nlayer}} \displaystyle\sum_{i} \left( w_{ji}^{\nlayer} z_{i}^{\nplayer{1}} \right) = \\
            & = \pd{}{w_{ji}^{\nlayer}} \left( w_{ji}^{\nlayer} z_{i}^{\nplayer{1}} + \displaystyle\sum_{k \neq i} \left( w_{jk}^{\nlayer} z_{k}^{\nplayer{1}} \right) \right) = \\
            & = \left( 1 \right) z_{i}^{\nplayer{1}} + \displaystyle\sum_{k \neq i} 0 = \\
            & = z_{i}^{\nplayer{1}}
        \end{split}
    \end{equation}

    \begin{equation}
        \pd{E_{n}}{w_{ji}} = \delta_{j}^{\nlayer} z_{i}^{\nplayer{1}}
        \label{eq:weight_partial_derivative_simplified}
    \end{equation}

    We can rewrite \eqref{eq:weight_partial_derivative} as
    \eqref{eq:weight_partial_derivative_simplified}.

    We call $ \delta_{j}^{\nlayer} $ \eqref{eq:errors} the errors. Because we
    already calculated every $ z_{i}^{\nplayer{1}} $ while forward propagating,
    we really just need to calculate the errors.

    The $ \delta_{j}^{\nlayer} $ we calculated is for the output layer. For the
    layer before that, we can also use the chain rule and calculate the other
    errors \eqref{eq:other_weight_partial_derivative}.

    \begin{equation}
        \begin{split}
            \delta_{j}^{\nplayer{1}} & = \pd{E_{n}}{a_{j}^{\nplayer{1}}} \\
            & = \displaystyle\sum_{k} \left( \pd{E_{n}}{a_{k}^{\nlayer}} \pd{a_{k}^{\nlayer}}{a_{j}^{\nplayer{1}}} \right) = \\
            & = \displaystyle\sum_{k} \left( \delta_{k}^{\nlayer} \pd{}{a_{j}^{\nplayer{1}}} \left( w_{kj}^{\nlayer} f^{\nplayer{1}} \left( a_{j}^{\nplayer{1}} \right) + \displaystyle\sum_{i \neq j} \left( w_{ki}^{\nlayer} z_{ki}^{\nplayer{1}} \right) \right) \right) = \\
            & = \displaystyle\sum_{k} \left( \delta_{k}^{\nlayer} w_{ki}^{\nlayer} f^{\prime \nplayer{1}} \left( a_{i}^{\nplayer{1}} \right)  \right) = \\
            & = f^{\prime \nplayer{1}} \left( a_{j}^{\nplayer{1}} \right) \displaystyle\sum_{k} \left( w_{kj}^{\nlayer} \delta_{k}^{\nlayer} \right)
        \end{split}
        \label{eq:other_weight_partial_derivative}
    \end{equation}

@@

    We may also accumulate gradients to apply it to the weights all at once
    \eqref{eq:batch}.

    \begin{equation}
        \pd{E}{w_{ji}^{\nlayer}} = \displaystyle\sum_{n} \pd{E_{n}}{w_{ji}^{\nlayer}}
        \label{eq:batch}
    \end{equation}

@@

    % \begin{figure}
    %     \begin{center}
    %         %\includegraphics[width=0.95\textwidth]{./res/double.jpeg}
    %         \input{./res/doubles.tex}
    %     \end{center}
    %     \caption{Change of error function on neural network to compute $ y = 2x
    %     $. The function y is the value the network is returning for one of the
    %     input training data.}\label{fig:doubles}
    % \end{figure}
    \begin{wrapfigure}{O}{0.5\textwidth}
        \begin{center}
            \input{./res/abs.tex}
        \end{center}
        \caption{Change of error function on neural network to compute $ y =
        \left| x \right| $. The function y is the value the network is
        returning for one of the input training data.}\label{fig:abs}
    \end{wrapfigure}
    \medskip
    % \begin{wrapfigure}{L}{0.48\textwidth}
    %     \begin{center}
    %         \input{./res/sin.tex}
    %     \end{center}
    %     \caption{Change of error function on neural network to compute $ y =
    %     \sin \left( x \right) $. The function y is the value the network is
    %     returning for one of the input training data.}\label{fig:sin}
    % \end{wrapfigure}
    % \begin{wrapfigure}{R}{0.48\textwidth}
    %     \begin{center}
    %         \input{./res/linear.tex}
    %     \end{center}
    %     \caption{Change of error function on neural network to compute $ y = ax
    %     + b $. The function y is the value the network is returning for one of
    %     the input training data.}\label{fig:linear}
    % \end{wrapfigure}
    % \begin{wrapfigure}{L}{0.48\textwidth}
    %     \begin{center}
    %         \input{./res/parabola.tex}
    %     \end{center}
    %     \caption{Change of error function on neural network to compute $ y =
    %     ax^{2} + bx + c $. The function y is the value the network is returning
    %     for one of the input training data.}\label{fig:parabola}
    % \end{wrapfigure}

@@

    There are so many think we can tweak. The learning rate, amount of layers
    and neurons, the training data, activation functions, initial weights and
    biases, error function. You really just need to stir the pile until the
    results look okay \cite{xkcd1838}.
